SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 21:12

Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.

@@

In this study, we evaluate the effects

@@

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period, to be used as reference.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data of AOD and water column from the AERONET monitoring network [@Giles2019; @Buis1998].
Our site participate in AERONET, where we operate a Cimel photometer since 2003.
We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We simulated the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.
For the atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of atmospheric clearness for the climatological conditions of the site.

@@

<!-- - rte_solver  disort -->
<!-- - geometry   pseudospherical -->
<!-- - mol_abs LOWTRAN -->

@@

>>>>

Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.

@@

In this study, we evaluated the effects of the clouds on th

@@

In order to identify CE cases, we need an approximation of the expected clear sky GHI
for the whole period of the study, with a temporal resolution of one minute.  Because
of the lack of exact data about atmospheric factors, responsible for the attenuation
of the solar radiation in the atmosphere, we can not recreate a minute by minute
representation of the reference radiation. Thus, we used some climatological data
with a radiation transfer model.

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the AERONET monitoring network [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003

For the production of .....

We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].  We simulated
the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the
range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.  For the
atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

@@

- rte_solver  disort
- geometry   pseudospherical
- mol_abs LOWTRAN

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases.
